Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-16 Manuscript/Manuscript.Rmd
attempt to add accolade to md plot

Ignoring the missingness in analyses can be extremely harmful to inferences. Complete case analysis (i.e., excluding all units with one or more missing entries) can introduce bias in statistical inference and lowers statistical power. Instead, the missingness should be accommodated *before* or *within* the analysis of scientific interest. Especially the former is very generic and popular ans is widely known as imputation. Imputing (i.e., filling in) the missing values seperates the missing data problem from the scientific problem: missing data are replaced by plausible values whereafter the completed data is analysed as if it were completely observed. The \proglang{R} package \pkg{mice} has become the de-facto standard for imputation by chained equations, which iteratively solves the missingness on a variable-by-variable basis. \pkg{mice} is known to yield valid inferences under many different missing data circumstances [@buur18]. In this paper, we'll discuss how to use \pkg{mice} in the context of multilevel data, under varying missing data mechanisms.^[Discuss missingness mechanisms before this point, add references @yuce08 and @hox15.]

>>>>

Ignoring the missingness in analyses can be extremely harmful to inferences. Complete case analysis (i.e., excluding all units with one or more missing entries) can introduce bias in statistical inference and lowers statistical power. Instead, the missingness should be accommodated *before* or *within* the analysis of scientific interest. Especially the former is very generic and popular and is widely known as imputation. Imputing (i.e., filling in) the missing values separates the missing data problem from the scientific problem: missing data are replaced by plausible values whereafter the completed data is analysed as if it were completely observed. The \proglang{R} package \pkg{mice} has become the de-facto standard for imputation by chained equations, which iteratively solves the missingness on a variable-by-variable basis. \pkg{mice} is known to yield valid inferences under many different missing data circumstances [@buur18]. In this paper, we'll discuss how to use \pkg{mice} in the context of multilevel data, under varying missing data mechanisms.^[Discuss missingness mechanisms before this point, add references @yuce08 and @hox15.]

### 2021-12-16 Manuscript/Manuscript.tex
attempt to add accolade to md plot

Ignoring the missingness in analyses can be extremely harmful to
inferences. Complete case analysis (i.e., excluding all units with one
or more missing entries) can introduce bias in statistical inference and
lowers statistical power. Instead, the missingness should be
accommodated \emph{before} or \emph{within} the analysis of scientific
interest. Especially the former is very generic and popular ans is
widely known as imputation. Imputing (i.e., filling in) the missing
values seperates the missing data problem from the scientific problem:
missing data are replaced by plausible values whereafter the completed
data is analysed as if it were completely observed. The \proglang{R}
package \pkg{mice} has become the de-facto standard for imputation by
chained equations, which iteratively solves the missingness on a
variable-by-variable basis. \pkg{mice} is known to yield valid
inferences under many different missing data circumstances
\citep{buur18}. In this paper, we'll discuss how to use \pkg{mice} in
the context of multilevel data, under varying missing data
mechanisms.\footnote{Discuss missingness mechanisms before this point,
  add references \citet{yuce08} and \citet{hox15}.}

>>>>

Ignoring the missingness in analyses can be extremely harmful to
inferences. Complete case analysis (i.e., excluding all units with one
or more missing entries) can introduce bias in statistical inference and
lowers statistical power. Instead, the missingness should be
accommodated \emph{before} or \emph{within} the analysis of scientific
interest. Especially the former is very generic and popular and is
widely known as imputation. Imputing (i.e., filling in) the missing
values separates the missing data problem from the scientific problem:
missing data are replaced by plausible values whereafter the completed
data is analysed as if it were completely observed. The \proglang{R}
package \pkg{mice} has become the de-facto standard for imputation by
chained equations, which iteratively solves the missingness on a
variable-by-variable basis. \pkg{mice} is known to yield valid
inferences under many different missing data circumstances
\citep{buur18}. In this paper, we'll discuss how to use \pkg{mice} in
the context of multilevel data, under varying missing data
mechanisms.\footnote{Discuss missingness mechanisms before this point,
  add references \citet{yuce08} and \citet{hox15}.}
